Leveraged Volume Sampling - Summary

### 2019-03-01 summary/paper-summary.tex
wip - rescaled vol sampling summary

            \begin{equation}
                P(\pi\in{[n]^k})\propto{det(\sum_{i=1}^{k}\frac{d}{l_{\pi_{i}}}x_{\pi_{i}}x_{\pi_{i}}^T)\prod_{i=1}^{k}\frac{l_{\pi_{i}}}{d}}, \text{where } l_{i}=x_{i}^T(X^TX)^{-1}x_{i}
            \end{equation}

@@

>>>>

            \begin{equation}
                P(\pi\in{[n]^k}) \propto det(\sum_{i=1}^{k}\frac{d}{l_{\pi_{i}}}x_{\pi_{i}}x_{\pi_{i}}^T)\prod_{i=1}^{k}\frac{l_{\pi_{i}}}{d}, \text{where } l_{i}=x_{i}^T(X^TX)^{-1}x_{i}
            \end{equation}

@@

    \section{Rescaled Volume Sampling Analysis}
        \textit{Leveraged Volume Sampling} is a specific case of \textit{Rescaled Volume Sampling}.
        Assume:
        \begin{equation*}
            \forall 1 \leq i \leq n: 0 \le q_{i} \leq 1, \text{ and } \sum_{i=1}^{n}q_{i} = 1
        \end{equation*}
        Then $(q_{i})_{i=1}^n$ defines a distribution over the lines of $X$.
        \textit{Rescaled Volume Sampling} suggests sampling $k$ rows with repetition from $X$ with the following proportion:
        \begin{equation}
            P(\pi \in [n]^k) \propto det(\sum_{i=1}^{k}\frac{1}{q_{\pi_{i}}}x_{\pi_{i}}x_{\pi_{i}}^T)\prod_{i=1}^{k}q_{\pi_{i}} = det(X^{T}Q_{\pi}X)\prod_{i=1}^{k}q_{\pi_{i}},
            \text{ where } Q=\sum_{i=1}^{k}\frac{1}{q_{\pi_{i}}}e_{\pi_{i}}e_{\pi_{i}}^T
        \end{equation}
        \begin{equation}
            w_{\pi}^\ast=(Q_{\pi}^{1/2}X)^{+}Q_{\pi}^{1/2}y
        \end{equation}

        By application of the following theorems the paper proves that $w_{\pi}^\ast$ is unbiased:
        \begin{itemize}
            \item The Cauchy-Binet theorem, decomposing $det(XQ_{\pi}X)$ as the sum of determinants of square sub-matrices of $X$, to calculate $\sum_{\pi \in [n]^k}det(X^{T}Q_{\pi}X)\prod_{i=1}^{k}q_{\pi_{i}}$.
            \item $E((I_{S}X)^+) = X^+$ for ordinary volume sampling to decompose both $w_{\pi}^\ast$ and $w^\ast$.
        \end{itemize}
